### 2023-04-20 paper.Rmd
some editing

where $t = 2$ gives the variance, $t = 3$ the skewness, and $t = 4$ the kurtosis [@joanes1998]. Thus, by changing $t$---the power of the deviation between mean and data points---we can use the k-plus logic to equalize any desired sample moment between groups. That is, we compute new variables for each original variable and for each distribution moment that should be considered in the anticlustering process. Analogously to the computation of, we could then define a $\mathit{SSE_{Skew}}$ for $t = 3$ or a $\mathit{SSE_{Kurtosis}}$ for $t = 4$. However, to formalize the computation of the k-plus criterion for an arbitrary number of distribution moments, some new notation has to be provided.

@@

Using the tensor $\mathbf{\hat{X}}_{T \times N \times P}$ and a vector of weights $\mathbf{w} = (w_1, \dots, w_T$), the generalized multicriterion for k-plus anticlustering $\mathit{SSE_{kplusGeneralized}}$ can be formalized:

@@

Here, $w_t$ is the weight associated with the $t$'th moment and $\overline{x}_{tj} ^{(k)}$ is mean for the $k$'th group on the $j$'th $t$-moment variable. Maximizing $\mathit{SSE_{kplusGeneralized}}$ can be used to minimize differences with regard to the first $T$ distribution moments between $K$ groups.

@@

Some simplifications in the computation of $\mathit{SSE_{kplusGeneralized}}$ can be arranged when ignoring the moment weights $\mathbf{w}$, e.g. by setting $w_t = 1$ ($t = 1, \dots, T$). This simplification leads to the *unweighted sum approach* for k-plus anticlustering. In this case, the additional dimension in $\mathbf{\hat{X}}_{T \times N \times P}$, representing distribution moments can be dropped; instead, the tensor is flattened into a two dimensional matrix, where the variables representing the additional distribution moments are appended to the original data matrix $\mathbf{X}_{N \times P}$, resulting in the augmented matrix $\mathbf{X'}_{N \times \mathit{TP}}$:

>>>>

where $t = 2$ gives the variance, $t = 3$ the skewness, and $t = 4$ the kurtosis [@joanes1998]. Thus, by changing $t$---the power of the deviation between mean and data points---we can use the k-plus logic to equalize any desired sample moment between groups. That is, we compute new variables for each original variable and for each distribution moment that should be considered in the anticlustering process. Analogously to the computation of $\mathit{SSE_{Var}}$, we could then define an $\mathit{SSE_{Skew}}$ using $t = 3$ or an $\mathit{SSE_{Kurtosis}}$ using $t = 4$. However, to formalize the computation of the k-plus criterion for an arbitrary number of distribution moments, some new notation has to be provided.

@@

Using $\mathbf{\hat{X}}_{T \times N \times P}$ and a vector of weights $\mathbf{w} = (w_1, \dots, w_T$), the generalized multicriterion for k-plus anticlustering $\mathit{SSE_{kplusGeneralized}}$ can be formalized:

@@

Here, $w_t$ is the weight associated with the $t$'th moment and $\overline{x}_{tj} ^{(k)}$ is the $k$'th group mean on the $j$'th $t$-moment variable. Maximizing $\mathit{SSE_{kplusGeneralized}}$ can be used to minimize differences with regard to the first $T$ distribution moments between $K$ groups.

@@

Some simplifications in the computation of $\mathit{SSE_{kplusGeneralized}}$ can be arranged when ignoring the moment weights $\mathbf{w}$, e.g. by setting $w_t = 1$ ($t = 1, \dots, T$). This simplification leads to the *unweighted sum approach* for k-plus anticlustering. In this case, the additional dimension in $\mathbf{\hat{X}}_{T \times N \times P}$, representing distribution moments can be dropped; instead, the tensor is flattened into a two-dimensional matrix, where the variables representing the additional distribution moments are appended to the original data matrix $\mathbf{X}_{N \times P}$, resulting in the augmented matrix $\mathbf{X'}_{N \times \mathit{TP}}$:
